---
title: "Assignment-1"
author:
  - name: Statistics-2
  - name: "B2230022"
  - name: "RKMVERI"
subtitle: "Bidit Sadhukhan"
format: 
  pdf: 
    documentclass: article
    geometry:
      - top=30mm
      - left=20mm
      - heightrounded
    fontfamily: libertinus
    colorlinks: true
date: "`r format(Sys.time(), '%B %d, %Y')`"
toc: true
editor: visual
---

## Question-1

Suppose that we are interested in assessing the effectiveness of a Social Skills Training (SST) program for

alcoholics that are in a rehabilitation program. Assume that 12 patients (the control group) participated in

the normal treatment program, and 11 patients (the test group) participated in the SST supplement in

addition to the normal treatment program. Based on the following data, can we conclude whether SST

training programme is effective or not?

|         |      |      |      |     |      |      |      |      |      |      |     |      |
|---------|------|------|------|-----|------|------|------|------|------|------|-----|------|
| Control | 1042 | 1617 | 1180 | 973 | 1552 | 1251 | 1151 | 1511 | 728  | 1079 | 951 | 1319 |
| Case    | 874  | 389  | 612  | 798 | 1152 | 893  | 541  | 741  | 1064 | 862  | 213 |      |

### Solution

For the given question, we will do the non-parametric test to check if the SST training programme is effective or not based on the given data because we are not given the information regarding the data distribution and the sample size is also small.

U statistic:

$$ U_{\text{mean}} = \frac{1}{2} \cdot n_1 \cdot n_2 $$

$$u_{\sigma} = \sqrt{\frac{n_1 \cdot n_2 \cdot (n_1 + n_2 + 1)}{n_1}}$$

Test Statistic:

$$
T = \frac{U - U_{\text{mean}}}{U_{\sigma}}
$$

```{r,}
# Control group data
control <- c(1042, 1617, 1180, 973, 1552, 1251, 1151, 1511, 728, 1079, 951, 1319)

# Case group data
case <- c(874, 389, 612, 798, 1152, 893, 541, 741, 1064, 862, 213)

# Perform Mann-Whitney U test
result <- wilcox.test(control, case)


```

------------------------------------------------------------------------

#### Output

```{r}
# Print the test results
print(result)

```

#### Comment

Based on the obtained p-value of 0.0009807, which is less than the conventional significance level of 0.05, we can reject the null hypothesis. Therefore, we have evidence to support the conclusion that there is a significant difference in the outcome between the control and case groups. This implies that the Social Skills Training (SST) program is effective in improving social skills for alcoholics in the rehabilitation program.

## Question-2

Some students of an Indian City, who were interviewed during a sample survey, are classified below

according to their smoking and tea drinking habits. Calculate Yule's measures of association.

|                    |        |            |
|--------------------|--------|------------|
|                    | Smoker | Non-smoker |
| Drinks-Tea         | 40     | 33         |
| Does not drink tea | 3      | 12         |

### Solution

```{r}
# Create a contingency table
smoking <- c(40, 3)
non_smoking <- c(33, 12)

contingency_table <- matrix(c(smoking, non_smoking), nrow = 2, ncol = 2, byrow = F)
colnames(contingency_table) <- c("Smoker", "Non-Smoker")
rownames(contingency_table) <- c("Drinks tea", "Does not drink tea")
print(contingency_table)

# Calculate Yule's measures of association
a <- contingency_table[1, 1]
b <- contingency_table[1, 2]
c <- contingency_table[2, 1]
d <- contingency_table[2, 2]

Q <- (a * d - b * c) / (a * d + b * c)
Y <- sqrt(Q)

```

------------------------------------------------------------------------

#### Output

```{r}

# Print the results
cat("Yule's Q:", Q, "\n")
cat("Yule's Y:", Y, "\n")

```

#### Comment

Yule's Q indicates a moderate positive association between smoking and tea drinking habits. This means that individuals who smoke are more likely to be tea drinkers, and vice versa. Yule's Y, which is the square root of Yule's Q, also shows a moderate association between smoking and tea drinking.
